---
title: "Replication of Study X by Sample & Sample (20xx, Psychological Science)"
author: "Replication Author[s] (contact information)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc_depth: 3
editor: 
  markdown: 
    wrap: 72
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

**Justification:** By replicating this project, I want to gain
experience running experiments with dyadic interaction. I am interested
in understanding how social norms form, and this kind of repeated games
are a common way to investigate this problem, hence will continue to be
useful in my research program.

**Stimuli and Procedures:** Participants will play a 2-player iterated
cooperative decision-making task which I will implement in Empirica.
Participants will be informed that they must select a parking spot in a
virtual parking lot over the course of several days. Different spots
will cost different amounts of a virtual currency (Monetary Units; price
remain fixed over days). Participants will be incentivized to minimize
cost paid as low cost paid corresponds to higher pay for participating
in the experiment. There are two zones in the lot: an orange zone and a
purple zone, and two parking spots per zone, and participants will
selecte a spot to park before seeing their partner's selection.
Participants will be informed that selecting the same color zone as
their partner would give them a “group discount”, but selecting the
exact same parking spot will incur a penalty price. After making their
decisions, participants were shown the actions that their partner took
and the price each participant paid.

Here are the links to the [repo](https://github.com/psych251/Yu2024) and
[paper](https://github.com/psych251/Yu2024/blob/main/original_paper/YuAndThompson.pdf).

## Project Progress

**Pilot A:** Results and preliminary graphs corresponding to the
original paper can be found at this [github
repo](https://github.com/yukam997/repetitive_coordination_game.git)
under the pilotA_results folder:

**Outcome Measure:** The success of the replication will be measured
based on how well the distribuion of strategies that the partners adopt
match the distribution from the original paper. More specifically, we
will use the same statistical analyses to compare the results obtained
in condition 3 with the results from condition 1 and 2 of the experiment
to see if the qualitative differences that they report replicate. The
main result we want to replicate is that "participants developed an
alternating norm more frequently than in the control (Condition 1)".
Additionally, we are also interested in the result that "participants
were less likely to converge on stable selection on orange compared to
the condition 1 (β=−0.75, CrI = \[−0.92,−0.59\]) and 2 (β=−0.29, CrI =
\[−0.46,−0.13\]) \* they failed to form any norm more frequently
compared to the control (β= 0.18, CrI = \[0.04, 0.31\])".

We will do the same statistical tests comparing results from other
conditions in the original paper with our replication results of
condition 3, to see whether these observations still hold.

We will also confirm whether "participants paid less over the course of
the game" still holds, which is a key indicator of whether participants
converged to systematic norms over time.

**Steps for Reproduction:**

-   Collecting data large-scale: I still need to set up the experiment
    on prolific to recruit participants, which I have no experience
    doing.

-   Analysis: I don't have a concrete idea of how to do the statistical
    analyses to measure the success of the replication outlined above.

-   Stimuli Refinement: The exact phrasing of the prompt and stimuli is
    different from the original paper. I will follow up and confirm with
    the original authors.

-   classifying strategies: I have written code to process csv's
    generated from participant's interaction history and classify
    strategies described in the paper. However, this may require minor
    alterations to match exactly the classification algorithm used by
    the original paper.

## Methods

### Power Analysis

Running the power analysis below shows that we should use 60 pairs,
hence recruit 120 participants to get a power of 0.8.

```{r}
library(pwr)
p1 <- 0.085 # probability of alternating on purple in condition 3
p2 <- 0.005  # probability of alternating on purple in condition 1

h <- ES.h(p1, p2)
result <- pwr.2p.test(h = h, n = 60, sig.level = 0.05, alternative = "greater")
result$power
```

### Planned Sample

We plan to run 120 participants.

### Materials

All materials - can quote directly from original article - just put the
text in quotations and note that this was followed precisely. Or, quote
directly and just point out exceptions to what was described in the
original article.

### Procedure

Can quote directly from original article - just put the text in
quotations and note that this was followed precisely. Or, quote directly
and just point out exceptions to what was described in the original
article.

### Analysis Plan

Can also quote directly, though it is less often spelled out effectively
for an analysis strategy section. The key is to report an analysis
strategy that is as close to the original - data cleaning rules, data
exclusion rules, covariates, etc. - as possible.

**Clarify key analysis of interest here** You can also pre-specify
additional analyses you plan to do.

### Differences from Original Study

Explicitly describe known differences in sample, setting, procedure, and
analysis plan from original study. The goal, of course, is to minimize
those differences, but differences will inevitably occur. Also, note
whether such differences are anticipated to make a difference based on
claims in the original article or subsequent published research on the
conditions for obtaining the effect.

### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data
collection.

#### Actual Sample

Sample size, demographics, data exclusions based on rules spelled out in
analysis plan

#### Differences from pre-data collection methods plan

Any differences from what was described as the original plan, or “none”.

## Results

### Data preparation

Data preparation following the analysis plan.

```{r include=F}
### Data Preparation

#### Load Relevant Libraries and Functions

#### Import data

#### Data exclusion / filtering

#### Prepare data for analysis - create columns etc.
```

### Confirmatory analysis

The analyses as specified in the analysis plan.

*Side-by-side graph with original graph is ideal here*

### Exploratory analyses

Any follow-up analyses desired (not required).

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary
result from the confirmatory analysis and the assessment of whether it
replicated, partially replicated, or failed to replicate the original
result.

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from
follow-up exploratory analysis, (b) assessment of the meaning of the
replication (or not) - e.g., for a failure to replicate, are the
differences between original and present study ones that definitely,
plausibly, or are unlikely to have been moderators of the result, and
(c) discussion of any objections or challenges raised by the current and
original authors about the replication attempt. None of these need to be
long.
